6CCS3PRJ \\\vspace{0.5cm} A Pragmatic Infrastructure Modelling and Verification Framework

### 2014-04-14 paper.tex
Fixed event float
streem -> stream D:

\begin{listing}[h]
  POST request to /events:
\begin{minted}[fontfamily=fi4]{json}
  {
    "type": "deployment",
    "host": "rb-production-01",
    "service": "example-service",
    "component": "application",
    "url": "https://github.com/joestanton/example-service/commits/0c4f3dd",
    "branch": "master",
    "build": "0c4f3dd",
    "committer": "Joe Stanton"
  }
\end{minted}
\end{listing}

Events provide the context needed to identify the cause of an issue, and discuss that issue with the relevant collaborator on the project.

@@

As well as the typical API resources previously discussed, a single endpoint is provided for clients to subscribe to a streem of changes. Where appropriate, all domain entities will be published to the changes stream as they are created, updated or deleted. Clients such as the Web UI can subscribe to these changes and update the user interface accordingly.

>>>>

\begin{listing}[htbp]
\begin{minted}[fontfamily=fi4]{json}
  {
    "type": "deployment",
    "host": "rb-production-01",
    "service": "example-service",
    "component": "application",
    "url": "https://github.com/joestanton/example-service/commits/0c4f3dd",
    "branch": "master",
    "build": "0c4f3dd",
    "committer": "Joe Stanton"
  }
\end{minted}
\end{listing}

@@

As well as the typical API resources previously discussed, a single endpoint is provided for clients to subscribe to a stream of changes. Where appropriate, all domain entities will be published to the changes stream as they are created, updated or deleted. Clients such as the Web UI can subscribe to these changes and update the user interface accordingly.
